---
title: "p8105_hw1_zl3544"
output: html_document
date: "2024-09-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is my solution for P8105 hw1

load the tidyverse function for hw1
```{r library, message=FALSE}
library(tidyverse)
```
###Problem 1

The problem focus on writing a short description of the penguins dataset which include:

* the data in this dataset, including names / values of important variables

* the size of the dataset

* the mean flipper length

* make a scatterplot

Load the penguins dataset from the palmerpenguins package:
```{r load_penguins}
data("penguins", package = "palmerpenguins")
```
##names of the dataset

The names of the data in penguins dataset is showed using the following code:
```{r plot_names, collapse=TRUE}
ls(penguins)
```
It shows that the names in the penguins dataset are: `r ls(penguins)`

##values of important variables in the dataset

"bill_depth_mm" is a `r class(pull(penguins, bill_depth_mm))` variable, 
the range is [`r  range(pull(penguins, bill_depth_mm), na.rm = TRUE)`]

"bill_length_mm" is a `r class(pull(penguins, bill_length_mm))` variable,
the range is [`r  range(pull(penguins, bill_length_mm), na.rm = TRUE)`]

"body_mass_g" is a `r class(pull(penguins, body_mass_g))` variable,
the range is [`r  range(pull(penguins, body_mass_g), na.rm = TRUE)`]

"flipper_length_mm" is a `r class(pull(penguins, flipper_length_mm))` variable,
the range is [`r  range(pull(penguins, flipper_length_mm), na.rm = TRUE)`]

"island" is a `r class(pull(penguins, island))` variable, 
the island are:`r paste(unique(pull(penguins, island)), collapse = ", ")`

"sex" is a `r class(pull(penguins, sex))` variable,
which includes: `r paste(unique(pull(penguins, sex)), collapse = ", ")`

"species" is a `r class(pull(penguins, species))` variable,
they are: `r paste(unique(pull(penguins, species)), collapse = ", ")`

"year" is a `r class(pull(penguins, year))` variable,
the data is from the year of `r paste(unique(pull(penguins, year)), collapse = ", ")`

##the size of the dataset

the size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns

##the mean flipper length

the mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

##making scatterplot

Use this code to make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x), and different species use the different color:
```{r}
#make a scatterplot
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "scatterplot of flipper_length_mm (y) vs bill_length_mm (x)",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  ) +
  theme_classic()
print(scatterplot)
# save the scatterplot
ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot, width = 6, height = 6)

```
### Problem 2
